Union and Intersection Contracts Are Hard, Actually

### 2021-09-16 paper.tex
Update paper.tex
Co-authored-by: Arnaud Spiwack <arnaud.spiwack@tweag.io>

The work by Dimoulas et al.~\cite{dimoulasESOP,dimoulasPOPL} presents
a complete study on systems that may execute (and potentially invalidate)
contracts inside other contracts, in particular through the study
of dependent function contracts.
Their ideas have the potential to help solve the problems outlined
on Sections \ref{sec:flat-and-inter} and \ref{sec:keil-thiemann},
however, we consider it's not clear how to leverage their techniques
for intersections.

>>>>

The work by Dimoulas et al.~\cite{dimoulasESOP,dimoulasPOPL} presents
a complete study on systems that may execute (and potentially invalidate)
contracts inside other contracts, in particular through the study
of dependent function contracts.
Their ideas have the potential to help solve the problems outlined
on Sections \ref{sec:flat-and-inter} and \ref{sec:keil-thiemann},
however, it isn't clear how to leverage their techniques
for intersections.
